### 2010-03-19 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: Single column figures, where possible.
IDesc@ICFP: pass over \note{}s. Remove non documented \propag usage.

From the examples above, we observe that data-types are defined by a
$\DSigma$ which first argument is a finite set of constructors. The
descriptions fitting into this pattern are called \emph{tagged}
description. Formally, we have:
\note{We have talked about a tagged description based on $\List (\UId
  \times \Desc)$. It makes the free monad easier to construct but,
  imho, considerably clutters anything else. I've reverted back to a
  more sigma-friendly presentation.}

@@

At this stage, we have recovered the data-types we are usually able to
define in simply-typed languages.
\note{pwm: Err, not quite --- not til we introduce $\DHindx{\!}{\!}$}

>>>>

From the examples above, we observe that data-types are defined by a
$\DSigma$ which first argument is a finite set of constructors. The
descriptions fitting into this pattern are called \emph{tagged}
description. Formally, we have:

@@

### 2010-03-19 papers/icfp-2010-desc/paper_type_theory.tex
IDesc@ICFP: pass over \note{}s. Remove non documented \propag usage.

\note{pwm: We should explain this new judgement form, specifically that
$\propag{}{}$ means `elaborates to'.}

\[
\Axiom{\Gamma ; \xS ; \Delta \Vdash \propag{\x}
                                           {\pull{\x}{S}}}
\]

@@

\[
\Rule{\Gamma ; \xS \Vdash \propag{\push{t}{T}}
                                 {t'}}
     {\Gamma \Vdash \propag{\push{\LAM{\x} t}{\PIS{\xS}{T}}}
                           {\PLAM{\x}{S} t'}} 
\]

In our formal presentation of the type theory, we were forced to
annotate lambda abstractions by the type of the domain. In a
bidirectional setting, the domain is provided by the $\Pi$ type we are
pushing the abstraction into. Hence we do not need the annotation.

>>>>

\[
\Rule{\Gamma ; \xS ; \Delta \vdash \Valid}
     {\Gamma ; \xS ; \Delta \vdash \Bhab{x}{S}}
\]

@@

\[
\Rule{\Gamma       \vdash \Type{S} \quad
      \Gamma ; \xS \vdash \Bhab{t}{T}}
     {\Gamma \vdash \Bhab{\PLAM{\x}{S} t}{\PIS{\xS} T}}
\]

Here, we are forced to annotate lambda abstractions by the type of the
domain. In a bidirectional setting, the domain is provided by the
$\Pi$ type we are pushing the abstraction into. Hence we do not need
the annotation.
